A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2020-06-02 paper/paper.comparison.tex
Work on comparison section

De Causmaecker and Berghe [ref] outlined a categorization
of nurse rostering problems using a similar approach used in personnel
scheduling,
based around the personnel environment, work characteristics and optimization
objective. [...]

[a few more papers on categorization, brief paragraph about each...]

@@

[outline and compare to papers with a similar categorization...]

>>>>

De Causmaecker and Berghe [ref] outline a categorization
of nurse rostering problems using a similar approach used in scheduling,
based around the personnel environment, work characteristics and optimization
objective. Previously, there was a lack of a central categorization for
nurse rostering problems found in the literature. Their work attempts
to address this, by creating a classification that takes into account
hard and soft constraints related to nurse preferences, consecutive 
assignments, coverage and various flexibilities in terms of shift and
skill types. They go on to describe where recent examples of the nurse rostering
literature can fit in their classification.

% DL - maybe this should be in complexity section?
Vanhoucke and Maenhout [ref] analyze and compare nurse rostering instances
based on complexity indicators arising from problem constraints. They consider
problem size (in terms of number of nurses, shifts and days), preference distribution
of the nurses, coverage distribution and time-related constraints (such as weekend
and consecutive constraints) as the four indicators for problem complexity.
Then, they generate sample problems corresponding to all four complexity indicators
and measure the effect of increasing complexity on CPU time required for solving each
problem.

[maybe 1 additional paragraph on categorization?]

@@

Using the classification in [ref-De Causmaecker and Berghe], we compare our clinician
scheduling problem and solution approach with existing literature. Azaiez and Al Sharif [ref]
describe a nurse rostering problem to schedule nurses on a per-day basis, for a total period
of 28 days. In this problem, they are required to assign a minimum number of staff members
per day, unlike in our clinician scheduling problem. Similar to our problem, they include
hard constraints to prevent consecutive assignments, and enforce a minimum and maximum 
number of shifts for each nurse. When formulating the optimization goal, Azaiez and Al Sharif
focus on balancing the workload among nurses, preventing day-night consecutive shifts and avoiding
off-on-off assignments. Their formulation does not incorporate nurse preferences
for time off into the model.

[...]
